A Large-scale Study of Polymorphism in R

### 2019-03-21 paper/main.tex
types

Another form of type information relates to metadata on values, and R allows
programmers to add said metadata in the form of {\it attributes}.  The
functionality to do so in R is through the \code{attributes(x)} and
\code{attr(x, "name")} functions.  \code{attributes}

Besides these primitive data types, R has an out-of-the-box data type called
the data frame for storing data, and this data type is essential to a large
part of R's functionality.  A data frame is a two-dimensional array where
each row represents an observation, with columns indicating the values of
some observation.  For example, our own analysis is written in R, and one of
our data frames has a row for each package analyzed, with columns for values
ranging from number of polymorphic functions, number of monomorphic
arguments, unique attribute patterns, etc.  \AT{Put a figure?}  Much of R's
base functionality, and indeed much of the functionality provided by
packages, operate on data frames.

\section{The Corpus}\label{sec:corpus}

>>>>

The addition of attributes lets programmers extend the set of types by
tagging data with user-defined attributes. For example, one could define a
vector of four values, \code{x<-c(1,2,3,4)} and then attach the attribute
\k{dim} with a pair of numbers as value: \code{attr(x,"dim")<-c(2,2)}.  From
that point, arithmetic functions will treat \k{x} as a 2x2 matrix. Another
attribute that can be set is the \k{class}.  This attribute can be bound to
a list of class names. For instance, \code{class(x)<-"human"}, set the class
of \k{x} to be \k{human}.  Attributes are thus used for object-oriented
programming. The S3 object system support single dispatch on the class of
the first argument of a function, whereas the S4 object system allows
multiple dispatch (on all arguments). Some of the most widely used data
type, such as data frames, leverage attributes. A data frame, for instance,
is a list of vectors with a class and a column name attribute.

\paragraph{Summary.} The most common values in R computations are vectorized
types. R programs do not have a way to constrain values to be scalar.
\k{NULL} is sometimes used to represent the case when no value is
available. \k{NA} is used within vector to represent missing observations.
Attributes can decorate values and are used as building blocks for
object-oriented programming. A potential type system for R could focus only
on the builtin types, if one wanted to strive for simplicity, or it could
try to capture attributes at the risk of increased complexity.

\newpage
\section{The Corpus}\label{sec:corpus}
